Robust Control of a Fluxonium Qubit

### 2020-09-30 paper/main.tex
before switch to z/2 in f2

%% ABSTRACT
\begin{abstract}
  %% - 1 + 2 topic importance
  %% - 1 what I have done
  %% - few sentences about primary results
  The ability to engineer high fidelity operations on quantum processors in the presence of
  calibration errors and decoherence remains the primary challenge requisite to achieving quantum advantage.
  Quantum optimal control (QOC) techniques have proven effective in realizing high fidelity operations,
  but they require exquisite calibration to be performant. In this work we employ robust trajectory optimization techniques
  to achieve high fidelity gates for parameter spreads on the order of $1\%$. 
  Additionally, current QOC techniques mitigate decoherence effects due to longitudinal relaxation by integrating
  the Lindblad master equation, which increases the computational complexity
  of the optimization algorithm.
  In this work we achieve a factor of $5$ increase in longitudinal relaxation times
  for the gate set of a fluxonium qubit
  using a computationally efficient metric in optimizaiton.
\end{abstract}

@@

%% S5
\section{Robustness to Parameter Deviations}
(Strategy) Magentic flux noise,
Johnson-Nyquist current noise present in the flux bias
lines, and temperature dependent gain fluctuations
may cause the flux amplitude to deviate from its
desired value by an amount $\delta a$. Additionally,
residual calibration errors and fluctuations may cause
the qubit frequency to deviate from its measured value
by an amount $\delta f_{q}$.

@@

(Comparison) To demonstrate the applicability of these techniques
to mitigate system parameter deviations,
we consider the task of achieving a single $X/2$
gate subject to a constant qubit frequency detuning
($f_{q} \gets f_{q} + \delta f_{q}$).
%% We use a compensating for off-resonance error
%% (CORPSE) dynamic decoupling pulse that is optimized
%% to mitigate first-order error arising due to the detuning.
%% The pulse is composed of
%% three rotations about the $\hat{x}$, $-\hat{x}$, and $\hat{x}$ axes
%% of the Bloch sphere
%% designed to compensate for erroneous rotations
%% (see Appendix).
We take $\sigma_{f_{q}} = 1\% f_{q}$ to be one standard devation, and equip
the sampling robustness methods accordingly.
For each method we compute the gate error for one simulated gate application
subject to the stated deviant dynamics.

@@

%% T2
\begin{table}
  \begin{tabular}{c | c | c | c}
    Method & ${\lvert \partial_{f_{q}} \ket{\psi} \rvert}^{2}$ ($10^{3}$)
    & ${\lvert \partial^{2}_{f_{q}} \ket{\psi} \rvert}^{2}$ ($10^{7}$)
    & ${\lvert \partial^{3}_{f_{q}} \ket{\psi} \rvert}^{2}$ ($10^{12}$)\\
    \hline
    D-2 & 8.706 & 8.331 & 3.692\\
    D-3 & 9.643 & 9.095 & 3.345\\
  \end{tabular}
  \caption{Norm of basis state derivatives undergoing a $X/2$ gate for the derivative methods at $t_{N} = 56.8$ns}
\end{table}

@@

%% TODO: maybe add new section
(Comparison) An additional task of interest is to mitigate
stochastic parameter deviations. For the fluxonium qubit, magnetic flux noise
acts to modify the flux amplitude from its intended value by an amount $\delta a$.
It is well studied that the spectral density of $\delta a$ follows a
1/$f$ distribution, consisting primarily of low frequency noise. We compare
the methods discussed for static parameter deviations to the task of
realizing a $X/2$ gate subject to 1/$f$ flux noise. We simulate successive
applications of the gate constructed by each method and measure the gate error
after each application (see Figure 3b). The system is subject to flux noise
$\delta a (t)$ that is generated from a standard normal distribution, normalized
by 1/$f^{1/2}$ in frequency space, and modulated by the experimentally obtained
flux noise amplitude $A_{\Phi} = 5.21 \mu \Phi_{0}$.

@@

%% S6
\section{Conclusion}
We have proposed some schemes and they work well.

%% ACK
\begin{acknowledgments}
  The authors would like to thank Helin Zhang for experimental assistance,
  and Stephen Lyon (maybe) and Daniel Weiss for useful discussions.
\end{acknowledgments}

>>>>

%% ABSTRACT
\begin{abstract}
  %% - 1 + 2 topic importance
  %% - 1 what I have done
  %% - few sentences about primary results
  The ability to engineer high fidelity operations on quantum processors in the presence of
  calibration errors and decoherence remains the primary challenge requisite to achieving quantum advantage.
  Quantum optimal control (QOC) techniques have proven effective in realizing high fidelity operations,
  but they require exquisite calibration to be performant. In this work we employ robust trajectory optimization techniques
  to achieve high fidelity gates for parameter spreads on the order of $1\%$. 
  Additionally, current QOC techniques mitigate decoherence effects due to longitudinal relaxation by integrating
  the Lindblad master equation, which increases the computational complexity
  of the optimization algorithm.
  In this work we achieve a factor of $5$ increase in longitudinal relaxation times
  for the gate set of a fluxonium qubit
  using a computationally efficient metric in optimization.
\end{abstract}

@@

%% S5
\section{Robustness to Static Parameter Deviations}
(Strategy) Uncertainty in the Hamiltonian parameters lead
to erroneous 
The uncertainty Hamiltonian parameters are known to
some finite experimental accuracy. Further,
experimental fluctuations may cause parameters to deviate
from their
the qubit frequency to deviate from its measured value
by an amount $\delta f_{q}$. There are other situations that
arise where this is useful, such as static amplitude
offsets or static gain offsets.

@@

(Comparison) To demonstrate the applicability of these techniques
to mitigate system parameter deviations,
we consider the task of achieving a single $X/2$
gate subject to a constant qubit frequency detuning
($f_{q} \gets f_{q} + \delta f_{q}$).
%% We use a compensating for off-resonance error
%% (CORPSE) dynamic decoupling pulse that is optimized
%% to mitigate first-order error arising due to the detuning.
%% The pulse is composed of
%% three rotations about the $\hat{x}$, $-\hat{x}$, and $\hat{x}$ axes
%% of the Bloch sphere
%% designed to compensate for erroneous rotations
%% (see Appendix).
We take $\sigma_{f_{q}} / f_{q} = 1\%$ to be one standard devation, and equip
the sampling robustness methods accordingly.
For each method we compute the gate error for one simulated gate application
subject to the stated deviant dynamics.

@@

@@

%% T2
\begin{table}
  \begin{tabular}{c | c | c}
    Method & ${\lvert \partial_{f_{q}} \ket{\psi_{N}} \rvert}^{2}$ ($10^{3}$)
    & ${\lvert \partial^{2}_{f_{q}} \ket{\psi_{N}} \rvert}^{2}$ ($10^{7}$)\\
    \hline
    D-1 & 2.509 & 13.292\\
    D-2 & 3.711 & 1.452\\
  \end{tabular}
  \caption{Norm of the first basis state's derivate with respect to the qubit frequency
    for $X/2$ gates optimized using the derivative methods. The norms are computed
    at the end of the gate's duration $t_{N} = 110$ns.}
\end{table}

\section{Robustness to Stochastic Parameter Deviations} %% S6
(Comparison) An additional task of interest is to mitigate
stochastic parameter deviations. For the fluxonium qubit, magnetic flux noise
acts to modify the flux amplitude from its intended value by an amount $\delta a$.
It is well studied that the spectral density of $\delta a$ follows a
1/$f$ distribution, consisting primarily of low frequency noise. We compare
the methods discussed for static parameter deviations to the task of
realizing a $X/2$ gate subject to 1/$f$ flux noise. We simulate successive
applications of the gate constructed by each method and measure the gate error
after each application (see Figure 3b). The system is subject to flux noise
$\delta a (t)$ that is generated from a standard normal distribution, normalized
by 1/$f^{1/2}$ in frequency space, and modulated by the experimentally obtained
flux noise amplitude $A_{\Phi} = 5.21 \mu \Phi_{0}$.

@@

%% S7
\section{Conclusion}
We have proposed some schemes and they work well.

%% ACK
\begin{acknowledgments}
  The authors would like to thank Helin Zhang for experimental assistance,
  and Daniel Weiss for useful discussions.
\end{acknowledgments}
